Lens Modeling in \sw

### 2013-09-07 text/tex/spaghetti.tex
SHELL FILE to create the plots. not really tested

The testing was done with a small number of volunteers ($N_v=4$) and a set of simulated configurations (N_{sim}=30) chosen to represent some typical configurations.
\todo{witch??}

>>>>

The testing was done with a small number of volunteers ($N_v=4$) and a set of simulated configurations ($N_{sim}=30$) chosen to represent some typical configurations.
